\chapter*{ABSTRACT}
\addcontentsline{toc}{chapter}{ABSTRACT}

This thesis designs and implements HearBridge, an interactive training system for people with hearing impairments based on HarmonyOS. The system aims to provide functional support for course learning, sign language gesture training, real-time recognition, sentence-level video recognition, training feedback, and resource management. Focusing on hearing-impaired assistance and training scenarios, HearBridge adopts a multi-end collaborative architecture consisting of a HarmonyOS mobile client, a Spring Boot backend service, a Vue-based web administration system, and a Python-based gesture recognition service. The mobile client provides course browsing, digital human gesture demonstration, gesture training, training result display, and sentence recognition result presentation. The backend service is responsible for user authentication, course and training data management, file resource management, recognition service invocation, and semantic enhancement. The web administration system maintains gesture categories, gesture resources, sample data, training tasks, and model versions. The Python recognition service supports keypoint extraction, feature conversion, model training, real-time word recognition, and offline sentence video recognition.

In terms of implementation, the system separates the user-side training process from the management-side model maintenance process. On the user side, the main workflow follows the pattern of standard gesture demonstration, user imitation training, and recognition-based feedback. Digital human resources are used to provide standard action demonstrations, while real-time recognition and video recognition are used to support training evaluation. On the management side, sample management, feature conversion, model training, and model version release are provided to support model updating and maintenance. For gesture recognition, the system uses MediaPipe to extract hand and pose keypoints and builds a temporal classification model based on TensorFlow for fixed-vocabulary gesture recognition. Furthermore, this thesis implements a limited-vocabulary sentence-level sign language video recognition pipeline. After receiving an uploaded sign language sentence video, the Python recognition service performs action window analysis, word-level candidate sequence generation, and Chinese gloss mapping. The Spring Boot backend then invokes a large language model for semantic correction and result organization, generating sentence-level recognition results that are easier for users to understand.

Testing and experimental results show that HearBridge can stably support core functions such as user login, course browsing, gesture training, real-time recognition, video upload recognition, resource management, sample management, model training, and model version release. Under limited-vocabulary experimental conditions, the sentence video recognition module completes the full workflow from video input to word sequence output, Chinese display, and semantic correction, verifying the feasibility of combining gesture recognition models with semantic post-processing in assistive communication scenarios. The implemented system provides a runnable engineering prototype for hearing-impaired training applications and lays a foundation for future extensions such as continuous sign language recognition, sign language assisted translation, digital human interaction, and personalized training feedback.

\vspace{1em}

\noindent\textbf{Keywords:} hearing-impaired assistance; HarmonyOS; gesture recognition; sentence-level video recognition; model version management
